---
title: "iniestat"
author: Romain Chailan - romain.chailan@gmail.com
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{iniestat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Install and load

```{r install-package, eval=FALSE}
# If you do not have it yet, download and install the package `iniestat` with
require(devtools)
devtools::install_github("rchailan/iniestat")
```

Then load the package in your environment with
```{r setup}
library(iniestat)
```

# Collect files

The very first function you want to use is `iniestat::collect_f24()`.
```{r collect-f24, eval=FALSE}
# if you want all the available game of the season `season`
collect_f24(user="XX12345", passwd="mypasswd", season=2020)

# if you want the game of id `match_id`
collect_f24(user="XX12345", passwd="mypasswd", match_id="7890")
 
# if you want several games, use `matches_id` as
collect_f24(user="XX12345", passwd="mypasswd", matches_id=c("7890", "7891", "7177"))
 
# if you need to specify the root url you can set
collect_f24(user="XX12345", passwd="mypasswd", season=2020, root_url="https://my_new_root_url")
```

You may want to choose to collect `F7` files associated with `F24` for further use. This is available with 
```{r collect-f7, eval=FALSE}
# if you want the game of id `match_id` and collect F7 files
collect_f24(user="XX12345", passwd="mypasswd", match_id="7890", store_f7 = TRUE)
```
This option works with all former configurations.

# Read F24 file(s)

With the function `iniestat::read_f24()` you can then read the files just downloaded.
It allows either to read one file or several files from a folder in one command only.

```{r read-files, eval=FALSE}
# To read one file from one match
my_events <- iniestat::read_f24(file_path = "my_f24.xml")

# To read several files from several match and stored in a directory
my_events_multi_games <- iniestat::read_f24(dir_path = "my_f24_data/")
```

The later function will read all files and concatenate the events into one tibble.

# Read OPT file(s)

Still in dev.